Staged Abstract Interpreters

### 2019-09-09 paper/10_intro.tex
typo
misc

Although the four artifacts may look dissimilar at first glance, they are in
fact all firmly rooted in the concrete semantics.  This observation provides a
way to abstract over the interpreter and achieve the flexibility of
reinterpreting the shared interpreter.  The generic interpreter returns a value
of monadic type, which vary based on semantics. The value domains
of the interpreter and the effects such as state and nondeterminism can all be
wrapped into this monadic type.  The binding-time abstraction is represented by
a higher-kinded type and injected into the monadic type.  The binding-times
control whether the interpreter produces values directly or generates code.

@@

\paragraph{Applications and Evaluation}
We evaluate the idea of staging an abstract interpreter through
case studies and an empirical performance evaluation.
1) We compare our approach with abstract compilation
\cite{Boucher:1996:ACN:647473.727587}, an implementation technique for
control-flow analyses. We show that by utilizing type-based stage
annotations, we can achieve the same optimizations. Meanwhile,
the analyzer does not need to change, except the addition of stage annotations,
thereby requiring significantly less engineering effort.
2) We extend the basic staged abstract interpreter to different flow
analyses, including a store-widened analysis, a context-sensitive
analysis, and abstract garbage collection.
3) We show that staging an abstract interpreter enables modular
compilation of an analysis to programs. Here we borrow the concept of
modular analysis, and show that the compiled analysis is reusable.
Therefore, the approach provides a modular way to create optimized
analysis code by mechanized reuse of a whole-program analyzer.
4) We empirically evaluate the performance improvements gained by staging,
showing an order of magnitude speedup.

>>>>

Although the four artifacts may look dissimilar at first glance, they are in
fact all firmly rooted in the concrete semantics.  This observation provides a
way to abstract over the interpreter and achieve the flexibility of
reinterpreting the shared interpreter.  The generic interpreter returns a value
of monadic types, which vary based on semantics. The value domains
of the interpreter and the effects such as state and nondeterminism can all be
wrapped into this monadic type.  The binding-time abstraction is represented by
a higher-kinded type and injected into the monadic type.  The binding-times
control whether the interpreter produces values directly or generates code.

@@

\paragraph{Applications and Evaluation}
We evaluate the idea of staging an abstract interpreter through
case studies and an empirical performance evaluation.
1) We compare our approach with abstract compilation
\cite{Boucher:1996:ACN:647473.727587}, an implementation technique for
control-flow analyses. We show that by utilizing type-based stage
annotations, we can achieve the same optimizations. Meanwhile,
the analyzer does not need to change (modulo the addition of stage annotations),
thereby requiring significantly less engineering effort.
2) We extend the basic staged abstract interpreter to different flow
analyses, including a store-widened analysis, a context-sensitive
analysis, and abstract garbage collection.
3) We show that staging an abstract interpreter enables modular
compilation of an analysis to programs. Here we borrow the concept of
modular analysis, and show that the compiled analysis is reusable.
Therefore, the approach provides a modular way to create optimized
analysis code by mechanized reuse of a whole-program analyzer.
4) We empirically evaluate the performance improvements gained by staging,
showing an order of magnitude speedup.
